1.3 Meet R - R Practice

### 2019-09-03 content/r/03-r-practice.Rmd
Fix typos on r practice
Fixed typos on R Practice 3, update class 3 notes

## 2. Use R's help functions to determine what the `paste()` function does. Then paste together your name from `me`.

@@

## 4. Find the mean of x with `mean()`.

## 5. Add up all the numbers from 18 to 763, then get the mean

@@

For the following questions, we will the `diamonds` dataset, included as part of `ggplot2`.

>>>>

## 2. Use R's help functions to determine what the `paste()` function does. Then paste together your first name and last name.

@@

## 4. Find the mean of `my_vector` with `mean()`.

## 5. Take all the integers from 18 to 763,^[Hint: use the `:` operator to create a sequence from a starting number to an ending number] then get the mean.

@@

For the following questions, we will use the `diamonds` dataset, included as part of `ggplot2`.
